PyQBench: a Python library for benchmarking gate-based quantum computers

### 2023-02-28 txt/manuscript.tex
Update last part of the CLI description

For synchronous experiment, the part of output looks similar to the one below. The whole YAML file can be seen in \ref{app:example}.
%Consider the particular experiment data
\begin{lstlisting}[language=Python]
data:
- target: 0
  ancilla: 1
  phi: 0.0
  results_per_circuit:
  - name: id
  histogram: {'00': 28, '01': 26, '10': 21, '11': 25}
  mitigation_info:
	target: {prob_meas0_prep1: 0.052200000000000024, prob_meas1_prep0: 0.0172}
	ancilla: {prob_meas0_prep1: 0.05900000000000005, prob_meas1_prep0: 0.0202}
  mitigated_histogram: {'00': 0.2637212373658018, '01': 0.25865061319892463, '10': 0.2067279352110304, '11': 0.2709002142242433}
\end{lstlisting}
	The data includes \texttt{target, ancilla, phi},
	and \texttt{results\_per\_circuit}.   The first three pieces of information have already been described. The last data  \texttt{results\_per\_circuit} gives us
	the following additional information:
	\begin{itemize}
		\item  \texttt{name}:  the information which measurement is used during experiment, either
		string \texttt{"u"} for $\PP_{U}$ or string \texttt{"id"} for $\PP_{\Id}$. In this example
		we consider $\PP_{\Id}$.
		\item \texttt{histogram}: the dictionary with measurement's outcomes. The keys represent possible bitstrings, whereas the values present number of occurrences.
		\item \texttt{mitigation\_info}:  \texttt{system.properties().qubits} contains information on the physical attributes of the qubits. This includes e.g. information about readout error. As shown below, the \texttt{readout\_error} is further partitioned into \texttt{prob\_meas0\_prep1} and \texttt{prob\_meas1\_prep0}, indicating the probability of preparing a given computational basis state, but measuring the orthogonal state.  The readout error is taken to be the average of these two values. Note that \texttt{prob\_meas0\_prep1} is usually the dominant factor in the readout error due to relaxation during the measurement process.  ~\cite{mthree, mthreepublication}
		\item mitigated\_histogram:  the histogram with measurement's outcomes after mitigation.
	\end{itemize}

@@

\subsubsection{Resolving asynchronous jobs}
If the status of jobs is \texttt{DONE}, we have to obtain measurements from the submitted jobs. This is done using the following command:
\begin{lstlisting}[language=Python]
qbench disc-fourier resolve async-results.yml resolved.yml
\end{lstlisting}
The resolved results, stored in \texttt{resolved.yml}, would look just like the experiment was run synchronously. More precisely, we should have a file containing measurement histograms, no matter if we run a synchronous or asynchronous experiment (see \ref{app:example}). Next, we can compute the discrimination probabilities.

\subsubsection{Computing probabilities}
Regardless of whether we use a synchronous or asynchronous approach, we can convert the resulting YML file \texttt{results.yml} to a CSV file by creating a result table in which we place the results of discrimination probabilities.
To construct a table with probabilities, you can use the following command
\begin{lstlisting}[language=Python]
qbench disc-fourier tabulate results.yml results.csv
\end{lstlisting}
A single row for each tuple of \texttt{(target, ancilla, phi)}.  The \texttt{ideal\_prob} 
column says the theoretical probability of correct discrimination whereas
the \texttt{disc\_prob} column contains the empirical discrimination probability. The \texttt{mit\_disc\_prob} column contains discrimination probability if Mthree mitigation was applied~\cite{mthree, mthreepublication}.
A sample csv file is provided below:
\begin{figure}[h!]
	\centering
	\includegraphics[scale=1]{results/async_result}
	\caption{Tabulate results}
	\label{fig:tabulateresults}
\end{figure}

>>>>

For synchronous experiment, the part of output looks similar to the one below. The whole YAML file can be seen in \ref{app:example}.
%Consider the particular experiment data
\begin{lstlisting}[language=Python]
data:
- target: 0
  ancilla: 1
  phi: 0.0
  results_per_circuit:
  - name: id
  histogram: {'00': 28, '01': 26, '10': 21, '11': 25}
  mitigation_info:
	target: {prob_meas0_prep1: 0.052200000000000024, prob_meas1_prep0: 0.0172}
	ancilla: {prob_meas0_prep1: 0.05900000000000005, prob_meas1_prep0: 0.0202}
  mitigated_histogram: {'00': 0.2637212373658018, '01': 0.25865061319892463, '10': 0.2067279352110304, '11': 0.2709002142242433}
\end{lstlisting}
	The data includes \texttt{target, ancilla, phi},
	and \texttt{results\_per\_circuit}.   The first three pieces of information have already been described. The last data  \texttt{results\_per\_circuit} gives us
	the following additional information:
	\begin{itemize}
		\item  \texttt{name}:  the information which measurement is used during experiment, either
		string \texttt{"u"} for $\PP_{U}$ or string \texttt{"id"} for $\PP_{\Id}$. In this example
		we consider $\PP_{\Id}$.
		\item \texttt{histogram}: the dictionary with measurements' outcomes. The keys represent
		possible bitstrings, whereas the values are the number of occurrences.
		\item \texttt{mitigation\_info}:  for some backends (notably for backends corresponding to
		IBM Q devices), \texttt{backends.properties().qubits} contains information that might be
		used for error mitigation using the MThree method \cite{mthree, mthreepublication}. If this
		info is available, it will be stored in the \texttt{mitigation\_info} field, otherwise this field will be absent.
		\item \texttt{mitigated\_histogram}: the histogram with measurements' outcomes after the error mitigation.
	\end{itemize}

@@

\subsubsection{Resolving asynchronous jobs}
For asynchronous experiments, the stored intermediate data has to be resolved in actual
measurements' outcomes. The following command will wait until all jobs are completed and then write
a result file.
\begin{lstlisting}[language=Python]
qbench disc-fourier resolve async-results.yml resolved.yml
\end{lstlisting}
The resolved results, stored in \texttt{resolved.yml}, would look just like if the experiment was
run synchronously. Therefore, the final results will look the same no matter in which mode the
benchmark was run, and hence in both cases the final output file is suitable for being an input for
the command computing the discrimination probabilities.

\subsubsection{Computing probabilities}
As a last step in the processing workflow, the results file has to be passed to \texttt{tabulate}
command:
\begin{lstlisting}[language=Python]
qbench disc-fourier tabulate results.yml results.csv
\end{lstlisting}
The resulting CSV file contains table with columns \texttt{target}, \texttt{ancilla}, \texttt{phi},
\texttt{ideal\_prob}, \texttt{disc\_prob} and, optionally, \texttt{mit\_disc\_prob}. Each row in the
table describes results for a tuple of \texttt{(target, ancilla, phi)}.  The reference optimal value
of discrimination probability is present in \texttt{ideal\_prob} column, whereas the obtained,
empirical discrimination probability can be found in the \texttt{disc\_prob} column. The
\texttt{mit\_disc\_prob} column contains empirical discrimination probability after applying the
Mthree error mitigation \cite{mthree, mthreepublication}, if it was applied.
A sample CSV file is provided below:
\begin{figure}[h!]
	\centering
	\includegraphics[scale=1]{results/async_result}
	\caption{Tabulated results}
	\label{fig:tabulateresults}
\end{figure}
